### 2014-08-08 analysis/figures/paper_figures.tex
Legend added
Fixex spacing a little bit
Documentation of figures

%% Rabbit 10 = Subject 1
%% Rabbit 9 = Subject 2
\begin{figure}[H]
\begin{center}
\includegraphics[scale=1.0]{surgical_methods.pdf}
\caption{Surgical approach, anatomy imaging.} % Figure 1
\end{center}
\end{figure}

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
\begin{center}
\begin{tabular}{c|cc|cc}
& \multicolumn{2}{c|}{Experiment} & \multicolumn{2}{c}{Control} \\
& Subject 1 & Subject 2 & Subject 1 & Subject 2 \\
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__off-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}}
\end{tabular}
\caption{Performance of the electrodes at the optimal location for the endovascular location compared with the performance on the live control trials. The SSAEP and SSVEP experimental trials for Subject 1 are shown for the mid-basilar location. All other performances are shown at the basilar tip position. In each of the experiments, all experimental trials elicited a much larger response than the control experiments, which indicates that true non-artifactual responses were recorded. In addition, the endovascular electrode achieved superior signals compared to the scalp electrodes for the VEP and SSAEP experiments.}
% Figure 2
\end{center}
\end{figure}
\setlength{\tabcolsep}{6pt}

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
\begin{center}
\begin{tabular}{c|cccc|cc}
         & \multicolumn{4}{c|}{Experiment}                       & \multicolumn{2}{c}{Control} \\
         &             &             &             &             & Live         & Dead \\
\hline
Location & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Basilar Tip  & Basilar Tip \\
Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
Time     & 0:00:00 & 2:15:44 & 3:57:12 & 4:50:05 & 0:18:05 & 5:24:40 \\ % TODO: time relative to anesthesia? relative to surgery
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep__off-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
\end{tabular}
\caption{Demonstration of position dependence for Subject 1. The performance of the endovascular electrode varies as its location is changed. The performance is consistent between the two basilar tip trials. }
% Figure 3
\end{center}
\end{figure}
\setlength{\tabcolsep}{6pt}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
\includegraphics[scale=0.5]{impedance.pdf}
\end{tabular}
\caption{Impedence characterization.} % Figure 4
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc|cc}
\raisebox{-0.5\height}{\multirow{3}{*}{
\begin{tabular}{c}
Cardiac-Aligned  Measurements \vspace{0.7cm} \\
\includegraphics[scale=0.64]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf}
\end{tabular}
}} &
& Raw Trace & VEP-Aligned \\
\hline
&
\raisebox{-0.5\height}{\rotatebox{90}{Contaminated}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__start-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled-crop.pdf}} \\
&
\raisebox{-0.5\height}{\rotatebox{90}{Cleaned}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} \\
\end{tabular}

\caption{Cardiac contamination and cleaning. 1076 trials for qrs mean} % Figure 5
\end{center}
\end{figure}

%% VEP 
%filename: _Tue_06.05.2014_11%3A17%3A10_vep_,    2 / 13
%Number of Trials: 153
%Number of Trials: 153
%filename: _Thu_15.05.2014_11%3A57%3A42_vep_,    4 / 16
%Number of Trials: 205
%Number of Trials: 206
%filename: _Thu_15.05.2014_14%3A13%3A26_vep_,    10 / 16
%Number of Trials: 192
%Number of Trials: 191
%filename: _Thu_15.05.2014_15%3A54%3A54_vep_,    12 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Thu_15.05.2014_16%3A47%3A47_vep_,    15 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Thu_15.05.2014_12%3A15%3A47_vep_ctr, 5 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Thu_15.05.2014_17%3A22%3A22_vep_,    16 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Tue_06.05.2014_11%3A25%3A22_vep_,    3 / 13
%Number of Trials: 153
%Number of Trials: 153
%filename: _Thu_15.05.2014_14%3A13%3A26_vep_,    10 / 16
%Number of Trials: 192
%Number of Trials: 191

>>>>

%% Rabbit 10 = Subject 1
%% Rabbit 9 = Subject 2
\begin{figure}[H]
\begin{center}
\includegraphics[scale=1.0]{surgical_methods.pdf}
\caption{Surgical approach, anatomy imaging.}
\label{fig:surgical}
% Figure 1
\end{center}
\end{figure}

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
\begin{center}
\includegraphics[]{../config/legend2.pdf} % TODO: vertical center
\hspace{0.3cm}
\begin{tabular}{c|cc|cc}
& \multicolumn{2}{c|}{Experiment} & \multicolumn{2}{c}{Control} \\
& Subject 1 & Subject 2 & Subject 1 & Subject 2 \\
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep__off-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}}
\end{tabular}
\caption{Performance of the electrodes at the optimal location for the endovascular location compared with the performance on the live control trials. The SSAEP and SSVEP experimental trials for Subject 1 are shown for the mid-basilar location. All other performances are shown at the basilar tip position. In each of the experiments, all experimental trials elicited a much larger response than the control experiments, which indicates that true non-artifactual responses were recorded. In addition, the endovascular electrode achieved superior signals compared to the scalp electrodes for the VEP and SSAEP experiments.}
\label{fig:both}
% Figure 2
\end{center}
\end{figure}
\setlength{\tabcolsep}{6pt}

\setlength{\tabcolsep}{2pt}
\begin{figure}[H]
\begin{center}
\begin{tabular}{c|cccc|cc}
         & \multicolumn{4}{c|}{Experiment}                       & \multicolumn{2}{c}{Control} \\
         &             &             &             &             & Live         & Dead \\
\hline
Location & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Basilar Tip  & Basilar Tip \\
Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
Time     & 0:00:00 & 2:15:44 & 3:57:12 & 4:50:05 & 0:18:05 & 5:24:40 \\ % TODO: time relative to anesthesia? relative to surgery
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep__off_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_15_54_54_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_16_47_47_vep__off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr_off-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_17_22_22_vep__off-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_12_19_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_58_34_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_17_12_38_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40_labelled-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_02_44_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_16_38_47_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../ssavep/matlab_data/_Thu_15_05_2014_17_18_01_ssvep_40-crop.pdf}}
\end{tabular}
\caption{Demonstration of position dependence for Subject 1. The performance of the endovascular electrode varies as its location is changed. The performance is consistent between the two basilar tip trials. }
\label{fig:position}
% Figure 3
\end{center}
\end{figure}
\setlength{\tabcolsep}{6pt}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc}
\includegraphics[scale=0.5]{impedance.pdf}
\end{tabular}
\caption{Impedance characterization.}
\label{fig:impedance}
% Figure 4
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{cc|cc}
\raisebox{-0.5\height}{\multirow{3}{*}{
\begin{tabular}{c}
Cardiac-Aligned  Measurements \vspace{0.7cm} \\
\includegraphics[scale=0.64]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__qrs-crop.pdf}
\end{tabular}
}} &
& Raw Trace & VEP-Aligned \\
\hline
&
\raisebox{-0.5\height}{\rotatebox{90}{Contaminated}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__start-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__cardiac_labelled-crop.pdf}} \\
&
\raisebox{-0.5\height}{\rotatebox{90}{Cleaned}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../qrs/matlab_data/_Thu_15_05_2014_14_13_26_vep__end-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.32]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep__labelled-crop.pdf}} \\
\end{tabular}
\caption{Cardiac contamination and cleaning. 1076 trials for qrs mean}
\label{fig:cardiac}
% Figure 5
\end{center}
\end{figure}

\section*{Figure Information}
This section is information about which trials where used for the figures and some information about the trials.
\begin{table}[H]
\begin{center}
\begin{tabular}{c|cc|cc}
& \multicolumn{2}{c|}{Experiment} & \multicolumn{2}{c}{Control} \\
& Subject 1 & Subject 2 & Subject 1 & Subject 2 \\
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_labelled-crop.pdf &
../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_17\_10\_vep\_-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr-crop.pdf &
../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_25\_22\_vep\_-crop.pdf \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_off\_labelled-crop.pdf &
../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_17\_10\_vep\_\_off-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr\_off-crop.pdf &
../vep/matlab\_data/\_Tue\_06\_05\_2014\_11\_25\_22\_vep\_\_off-crop.pdf \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_26\_54\_ssaep\_86\_labelled-crop.pdf &
../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_37\_22\_ssaep\_86-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_26\_26\_ssaep\_ctr\_86-crop.pdf &
../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_42\_15\_ssaep\_86-crop.pdf \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_20\_24\_ssvep\_40\_labelled-crop.pdf &
../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_14\_51\_ssvep\_40-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_13\_26\_ssvep\_ctr\_40-crop.pdf &
../ssavep/matlab\_data/\_Tue\_06\_05\_2014\_11\_23\_01\_ssvep\_40-crop.pdf
\end{tabular}
\end{center}
\caption{Figure \ref{fig:both} files used to generate plot.}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{c|cccc|cc}
         & \multicolumn{4}{c|}{Experiment}                       & \multicolumn{2}{c}{Control} \\
         &             &             &             &             & Live         & Dead \\
\hline
Location & Basilar Tip & Mid-Basilar & VB Junction & Basilar Tip & Basilar Tip  & Basilar Tip \\
Time     & 11:57:42    & 14:13:26    & 15:54:54    & 16:47:47    & 12:15:47     & 17:22:22 \\
Time     & 0:00:00 & 2:15:44 & 3:57:12 & 4:50:05 & 0:18:05 & 5:24:40 \\ % TODO: time relative to anesthesia? relative to surgery
\hline
\raisebox{-0.5\height}{\rotatebox{90}{VEP On}} &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_labelled-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_14\_13\_26\_vep\_-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_15\_54\_54\_vep\_-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_16\_47\_47\_vep\_-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_17\_22\_22\_vep\_-crop.pdf \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP Off}} &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_11\_57\_42\_vep\_\_off\_labelled-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_14\_13\_26\_vep\_\_off-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_15\_54\_54\_vep\_\_off-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_16\_47\_47\_vep\_\_off-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_12\_15\_47\_vep\_ctr\_off-crop.pdf &
../vep/matlab\_data/\_Thu\_15\_05\_2014\_17\_22\_22\_vep\_\_off-crop.pdf \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_31\_02\_ssaep\_86\_labelled-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_26\_54\_ssaep\_86-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_12\_19\_ssaep\_86-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_58\_34\_ssaep\_86-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_26\_26\_ssaep\_ctr\_86-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_17\_12\_38\_ssaep\_86-crop.pdf \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_08\_22\_ssvep\_40\_labelled-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_14\_20\_24\_ssvep\_40-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_02\_44\_ssvep\_40-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_16\_38\_47\_ssvep\_40-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_12\_13\_26\_ssvep\_ctr\_40-crop.pdf &
../ssavep/matlab\_data/\_Thu\_15\_05\_2014\_17\_18\_01\_ssvep\_40-crop.pdf
\end{tabular}
\caption{Figure \ref{fig:position} files used to generate plot.}
\label{fig:position}
% Figure 3
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{cc|cc}
Filename & Index & VEP On & VEP Off \\
\hline
\_Tue\_06.05.2014\_11\%3A17\%3A10\_vep\_ & 2 / 13 & 153 & 153 \\
\_Thu\_15.05.2014\_11\%3A57\%3A42\_vep\_ & 4 / 16 & 205 & 206 \\
\_Thu\_15.05.2014\_14\%3A13\%3A26\_vep\_ & 10 / 16 & 192 & 191 \\
\_Thu\_15.05.2014\_15\%3A54\%3A54\_vep\_ & 12 / 16 & 208 & 208 \\
\_Thu\_15.05.2014\_16\%3A47\%3A47\_vep\_ & 15 / 16 & 208 & 208 \\
\_Thu\_15.05.2014\_12\%3A15\%3A47\_vep\_ctr & 5 / 16 & 208 & 208 \\
\_Thu\_15.05.2014\_17\%3A22\%3A22\_vep\_ & 16 / 16 & 208 & 208 \\
\_Tue\_06.05.2014\_11\%3A25\%3A22\_vep\_ & 3 / 13 & 153 & 153 \\
\_Thu\_15.05.2014\_14\%3A13\%3A26\_vep\_ & 10 / 16 & 192 & 191
\end{tabular}
\end{center}
\caption{Number of Trials Averaged for VEP (this may slightly smaller than the number of LED on/off, since some segments might have been skipped)}
\end{table}
%% VEP 
%filename: _Tue_06.05.2014_11%3A17%3A10_vep_,    2 / 13
%Number of Trials: 153
%Number of Trials: 153
%filename: _Thu_15.05.2014_11%3A57%3A42_vep_,    4 / 16
%Number of Trials: 205
%Number of Trials: 206
%filename: _Thu_15.05.2014_14%3A13%3A26_vep_,    10 / 16
%Number of Trials: 192
%Number of Trials: 191
%filename: _Thu_15.05.2014_15%3A54%3A54_vep_,    12 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Thu_15.05.2014_16%3A47%3A47_vep_,    15 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Thu_15.05.2014_12%3A15%3A47_vep_ctr, 5 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Thu_15.05.2014_17%3A22%3A22_vep_,    16 / 16
%Number of Trials: 208
%Number of Trials: 208
%filename: _Tue_06.05.2014_11%3A25%3A22_vep_,    3 / 13
%Number of Trials: 153
%Number of Trials: 153
%filename: _Thu_15.05.2014_14%3A13%3A26_vep_,    10 / 16
%Number of Trials: 192
%Number of Trials: 191
